Big Brother Is Watching

### 2015-11-05 manuscript.tex
commit

>>>>

\section{Randomized Blocking}
Another randomized strategy is to divide Manhattan into rectangular blocks as before, but instead of putting all of the blocks of the same size contiguously, we will randomize their positions (as long as the rectangles still tile the grid). In addition, the drones traversing the rectangles could reverse position every so often (although the blocks would have to be small enough that they could do this without leaving part of the block uninspected for more than 15 minutes). Finally, the positions of the rectangles could switch at random times; the drones assigned to each block would simply start moving in a different pattern as the position and/or shape of the block that they were assigned to changes.
